### 2025-08-26 getting-started.qmd
20250826 - formatting

In base `R`, you can perform piping with the `base::\`|>\`` expression.
In `tidyverse`, you can perform piping with the `magrittr::\`%>%\`` expression.

>>>>

In base `R`, you can perform piping with the ``base::`|>` `` expression.
In `tidyverse`, you can perform piping with the ``magrittr::`%>%` `` expression.
